### 2023-11-06 main.tex
^'^'

\subsection{Integrable process on a line segment}\label{subsection-description-process-LINE}
In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$. These reservoirs, exchanging particle with the external environment, put the chain out of equilibrium. The Hamiltonian that we consider here is obtained from \eqref{OriginalHamiltonian} assuming that the conductances are
\begin{equation}
	\omega_{x,y}=\begin{cases}
		1 \quad \text{if}\quad |x-y|=1\\
		0\quad \text{otherwise}
	\end{cases}
\end{equation}
and the coupling to reservoirs are
\begin{equation}
	\Gamma_{x}=\begin{cases}
		1\quad \text{if} \quad x\in \{1,L\}\\
		0\quad \text{otherwise}
	\end{cases}
\end{equation}
The case $\nu=1$, i.e. one particle at most for each site, is special. We will consider this extensively in Section \ref{sectionIntegrabiliy}.
We will denote the element of the representation of the $gl(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e. $(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in the first fundamental representation of the algebra.
The Hamiltonian now reads
\begin{equation}\label{hamiltonian}
	H=H_{left}+H_{bulk}+H_{right}
\end{equation}
where
\begin{equation}
	H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
\end{equation}
Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the vertices of the edge $x,x+1$) of the two-site Hamiltonian
\begin{equation}\label{H-corsivo}
	\begin{split}
		\mathcal{H}=P-\id
	\end{split}
\end{equation}
with 
\begin{equation}
	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}.
\end{equation} 
The action of $\mathcal{H}$ amounts to the permutation of the occupations of the two sites, i.e.
\begin{equation}
	\begin{split}
		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle\dt
	\end{split}
\end{equation}
The boundary terms are given by 
\begin{equation}
	H_{left}=\begin{pmatrix}
		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
		\alpha_{2}&\alpha_{2}-1&\alpha_{2}&\ldots&\ldots&\alpha_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\alpha_{N-1}&\alpha_{N-1}&\ldots&\ldots&\alpha_{N-1}-1&\alpha_{N-1}\\
		\alpha_{N}&\alpha_{N}&\ldots&\ldots&\alpha_{N}&\alpha_{N}-1
	\end{pmatrix}
\end{equation}
\begin{equation}
	H_{right}=\begin{pmatrix}
		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
		\beta_{2}&\beta_{2}-1&\beta_{2}&\ldots&\ldots&\beta_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\beta_{N-1}&\beta_{N-1}&\ldots&\ldots&\beta_{N-1}-1&\beta_{N-1}\\
		\beta_{N}&\beta_{N}&\ldots&\ldots&\beta_{N}&\beta_{N}-1
	\end{pmatrix}
\end{equation}
where, without loss of generality,  we assume that the parameters satisfy
\begin{equation}\label{ratesConditions}
	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1\;.
\end{equation} 
We define also 
\begin{equation}\label{lambdaConditions}
	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}\lambda_{a}=0\,.
\end{equation}
Under these assumption the Hamiltonian \ref{hamiltonian} is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).

@@

\subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE}. We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. Now we assume the hard-core exclusion rule, i.e. $\nu=1$. The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$. Duality result stated in Subsection \ref{statementDualitySubsection} can be adapted. The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively. The matrix $R_{x}$ defined in \eqref{Revmatrix} 
reduces to the identity, therefore the relation between the generators of the algebra and its transposed reduces to
\begin{equation}\label{transpostionPropertyFund}
	e_{ab}^T= e_{ba}\dt
Therefore, duality matrix reads
	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\otimes \mathcal{D}_{L+1}
where $\mathcal{D}_{0}$ and $\mathcal{D}_{L+1}$ are given in \eqref{dualityMatrix2}. 
The elements of this duality matrix are given by
\begin{equation}\label{ElementsDualityMatrixChain}
	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
The dual Hamiltonian is
	\widetilde{H}=\widetilde{H}_{left}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{right}
where $\mathcal{H}$ is defined in \eqref{H-corsivo} and 
\begin{equation}\label{boundary-H-dual-chain}
	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((\mathbf{a}{\dagger})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((\mathbf{a}^{\dagger})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
In the long-time limit the dual process voids the chain, i.e. all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$. We also notice that, up the the bosonic creation operators $(a^{\dagger})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular. This simplification will be crucial in Sections \ref{sectionIntegrabiliy}.\\
In this notation, the elements of the duality matrix reads
\begin{equation}\label{ElementsDualityMatrixChain_1}
	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. We pick the dual configuration $\xi=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
	\bm{\xi}=\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain} read
	D(\bm{\tau},\bm{\hat{\xi}})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{y_{k}},s_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\dt
Denoting the $m$-point correlations in the non-equilibrium steady state (NESS) by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]$ we have 
%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$). Therefore, we have the following equalities
\begin{equation}\label{CorrelationByABS-prob}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{\hat{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{\hat{\xi}}(t))\right]
	\\&=\sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(c_{k}\delta^{0}_{a_k}+(1-c_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
 namely the joint probability of having, for all $k=1,\ldots,m$, $c_{k}$ particles of species $a_{k}$ initially positioned at site $x_{k}$ are absorbed at left and $1-c_{k}$ of the same particles absorbed at right. Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.

@@

 Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations.
\subsection{The explicit form of the steady state}\label{subsection-exact}
The MPA gives an abstract form of the steady state in terms of an algebra of operators. This path has been followed in \cite{vanicat2017exact} to find one and two-point correlations. 
Here we follow the same approach. We will show that the existence of absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the  use of commutators in the

@@

The computation are organized as follows: we first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$. Second, we compute right eigenvector with vanishing eigenvalue of $H^{''}$ exploiting the simpler commutators. Finally, we invert the similarities and retrieve the right eigenvector of $H^{'}$ with vanishing eigenvalue and  the arbitrary correlations in the non-equilibrium steady state. The explicit expression of the steady state $|\Psi\rangle$ of $H$ is reported in Appendix \ref{appB}.

@@

@@

\textbf{Remark:} If we consider the case $N=2$ we have that, for an arbitrary configuration $\bm{\tau}$, we define $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites and the remaining $L-|\bm{\tau}|$ empty. We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones. We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,|\tau|\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$. These $(\ell_{i})_{i\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected. For each $\ell_{i}$ we introduce $x_{\ell_{i}}$, i.e. the coordinate where the particle with label $\ell_{i}$ is placed. We this notation we have that 
	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)\dt
%We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, and such that $\ell_{i}\in\{1,\ldots,|\bm{\tau}|\}$ for all $i\in\{1,\ldots,q\}$. Therefore, we can label each occupied coordinate by $x_{\ell_{i}}$. 

@@

Therefore, using equation \eqref{ABS_intermediate} and observing that $c_{x}\delta_{\tau_{x},N} =\delta_{\tau_{x},N}$, we obtain 
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\tau_{x}}^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
	\end{split}
\end{equation} 
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
\begin{flushright}
    $\square$
\end{flushright}

\subsection{Explicit formula for the steady state $|\Psi\rangle$}
{\color{blue}can we proceed as above? using sth similar to \eqref{goodTP-S2}}

@@

\subsection{Exact steady state correlations}\label{correlation-section}

>>>>

\subsection{Integrable process on a line segment}\label{subsection-description-process-LINE}
In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$. These reservoirs, exchanging particle with the external environment, put the chain out of equilibrium. The Hamiltonian that we consider here is obtained from \eqref{OriginalHamiltonian} assuming that the conductances are
	\omega_{x,y}=\begin{cases}
		1 \quad \text{if}\quad |x-y|=1\\
		0\quad \text{otherwise}
and the coupling to reservoirs are
	\Gamma_{x}=\begin{cases}
		1\quad \text{if} \quad x\in \{1,L\}\\
		0\quad \text{otherwise}
The case $\nu=1$, i.e. one particle at most for each site, is special. We will consider this extensively in Section \ref{sectionIntegrabiliy}.
We will denote the element of the representation of the $gl(N)$  Lie algebra with $\nu=1$ by lowercase letters, i.e. $(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in the first fundamental representation of the algebra.
The Hamiltonian now reads
\begin{equation}\label{hamiltonian}
	H=H_{left}+H_{bulk}+H_{right}
	H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the vertices of the edge $x,x+1$) of the two-site Hamiltonian
\begin{equation}\label{H-corsivo}
		\mathcal{H}=P-\id
with 
	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}.
 In this context, it will be useful to introduce the following notation for the occupation variable of the process. Each configuration is denoted by
with $\tau_{x}\in \{1,\ldots,N\}$, $\forall x\in \{1,\ldots,L\}$. The configuration $\bm{n}$, introduced in Subsection \ref{subsectionGeneratorStr} and $\bm{\tau}$ are related by 
The state space of the process is now given in terms of $\bm{\tau}$ by
	\Omega=\bigtimes_{x=1}^{L}\Omega_{x}\qquad \Omega_{x}=\left\{|\tau_{x}\rangle\;:\; \tau_{x}\in\{1,\ldots,N\}\right\}
In all situations where we consider the integrable chain, we will use this notation for the configuration variable.\\ 
The action of $\mathcal{H}$ amounts to the permutation of the occupations of the two sites, i.e.
		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle\dt
The boundary terms are given by 
	H_{left}=\begin{pmatrix}
		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
		\alpha_{2}&\alpha_{2}-1&\alpha_{2}&\ldots&\ldots&\alpha_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\alpha_{N-1}&\alpha_{N-1}&\ldots&\ldots&\alpha_{N-1}-1&\alpha_{N-1}\\
		\alpha_{N}&\alpha_{N}&\ldots&\ldots&\alpha_{N}&\alpha_{N}-1
	H_{right}=\begin{pmatrix}
		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
		\beta_{2}&\beta_{2}-1&\beta_{2}&\ldots&\ldots&\beta_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\beta_{N-1}&\beta_{N-1}&\ldots&\ldots&\beta_{N-1}-1&\beta_{N-1}\\
		\beta_{N}&\beta_{N}&\ldots&\ldots&\beta_{N}&\beta_{N}-1
where, without loss of generality,  we assume that the parameters satisfy
\begin{equation}\label{ratesConditions}
	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1\;.
We define also 
\begin{equation}\label{lambdaConditions}
	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}\lambda_{a}=0\,.
Under these assumption the Hamiltonian \ref{hamiltonian} is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).

@@

\subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
Here we consider the chain defined in Subsection \ref{subsection-description-process-LINE}. We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. Now we assume the hard-core exclusion rule, i.e. $\nu=1$. The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$. Duality result stated in Subsection \ref{statementDualitySubsection} can be adapted. The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively. The matrix $R_{x}$ defined in \eqref{Revmatrix} 
reduces to the identity, therefore the relation between the generators of the algebra and its transposed reduces to
\begin{equation}\label{transpostionPropertyFund}
	e_{ab}^T= e_{ba}\dt
\end{equation}
Therefore, duality matrix reads
\begin{equation}
	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\otimes \mathcal{D}_{L+1}
\end{equation}
where $\mathcal{D}_{0}$ and $\mathcal{D}_{L+1}$ are given in \eqref{dualityMatrix2}. 
The elements of this duality matrix are given by
\begin{equation}\label{ElementsDualityMatrixChain_1}
	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
\end{equation}
%\begin{equation}\label{ElementsDualityMatrixChain}
%	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
The dual Hamiltonian is
\begin{equation}
	\widetilde{H}=\widetilde{H}_{left}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{right}
\end{equation}
where $\mathcal{H}$ is defined in \eqref{H-corsivo} and 
\begin{equation}\label{boundary-H-dual-chain}
	\widetilde{H}_{left}=\sum_{a=1}^{N-1}\left((\mathbf{a}{\dagger})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{right}=\sum_{a=1}^{N-1}\left((\mathbf{a}^{\dagger})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
\end{equation}
In the long-time limit the dual process voids the chain, i.e. all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$. We also notice that, up the the bosonic creation operators $(a^{\dagger})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular. This simplification will be crucial in Sections \ref{sectionIntegrabiliy}.\\

%In this notation, the elements of the duality matrix reads
%\begin{equation}\label{ElementsDualityMatrixChain_1}
%	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
%\\
Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. We pick the dual configuration $\xi=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 
\begin{equation}
	\bm{\xi}=\begin{cases}
		\xi_{a}^{x}=1\qquad \text{if}\;x=x_{k}\;\text{and}\; a=a_{k}\\
		\xi_{a}^{x}=0\qquad \text{otherwise}
	\end{cases}
\end{equation}
For any $\bm{\tau}\in \Omega$ the elements of the duality matrix defined in \eqref{ElementsDualityMatrixChain} read
\begin{equation}
	D(\bm{\tau},\bm{\xi})=\prod_{k=1}^{m}\mathbbm{1}_{\{\delta_{\tau_{x_{k}},a_{k}}=1\}}=\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\dt
\end{equation}
Denoting the $m$-point correlations in the non-equilibrium steady state (NESS) by $\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]$ we have 
%To compute the steady state $m$-point correlations of the process $\bm{n}(t)$ we recall that the dual process eventually voids the chain (by putting all particles in the extra-sites $0$ and $L$). Therefore, we have the following equalities
\begin{equation}\label{CorrelationByABS-prob}
	\begin{split}
\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]
	\\&=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})
\end{split}
\end{equation}
where
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{k}\delta^{0}_{a_k}+(1-t_{k})\delta^{L+1}_{a_k}\right)\lvert \bm{\xi}(0)=\hat{\bm{\xi}}\right)
\end{equation}
 namely the joint probability of having, for all $k=1,\ldots,m$, $t_{k}$ particles of species $a_{k}$ initially positioned at site $x_{k}$ are absorbed at left and $1-t_{k}$ of the same particles absorbed at right. Therefore, by computing these absorption probabilities we determine the arbitrary non-equilibrium steady state correlations of the integrable multi-species stirring process.

@@

 Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations. \\ \\The MPA gives an abstract form of the non-equilibrium steady state in terms of an algebra of operators. However, the computation of exact correlations are in general involving. 
 We will show that the existence of absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the use of commutators in the

@@

\subsection{Exact correlations in the non-equilibrium steady state}\label{subsection-exact}
In this section we write a formula for the stationary non-equilibrium steady state correlations between $m$- points of the chain, each of them occupied by a non-empty species, i.e. a species with label from $1$ to $N-1$. %This is motivated by the interest of understanding how actual particles of the chain are correlated among each others and also because in the steady state the holes depends on the occupation of all other species, as a consequence of the constraint $n_{N}^{x}=1-\sum_{b=1}^{N-1}n_{b}^{x}$ for arbitrary $x\in \{1,\ldots,L\}$.
 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$. In each of these points there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$. Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by
\paragraph{Absorption probabilities}
The absorption probabilities are given by  
\begin{equation}\label{abs-probabilities}
where $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$. \\ \\
\textbf{Proof of \eqref{abs-probabilities}}: 
 using the binomial theorem we rewrite the \eqref{exactCorrelations} as 
%The elements of the duality matrix in this integrable case are given in equation \eqref{ElementsDualityMatrixChain_1}. Thus we have that 
%	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{y_{k}}=s_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}D(\tau,\hat{\bm{\xi}})\langle\tau|\Psi\rangle
%where the dual configuration is $\hat{\bm{\xi}}=\sum_{k=1}^{m}\delta^{y_{k}}_{s_{k}}$. 
Therefore, comparing the above formula and \eqref{absProbabilitiesIntegrable}, we can read off the absorption probabilities. 
\subsubsection{Explicit examples of non-equilibrium steady state correlations}
%The computation are organized as follows: we first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$. Second, we compute right eigenvector with vanishing eigenvalue of $H^{''}$ exploiting the simpler commutators. Finally, we invert the similarities and retrieve the right eigenvector of $H^{'}$ with vanishing eigenvalue and  the arbitrary correlations in the non-equilibrium steady state. The explicit expression of the steady state $|\Psi\rangle$ of $H$ is reported in Appendix \ref{appB}. 

@@

\subsection{Proof of th exact correlations in the non-equilibrium steady state}
[ADD TEXT]

@@

@@

Therefore, using equation \eqref{ABS_intermediate} and observing that $c_{x}\delta_{\tau_{x},N} =\delta_{\tau_{x},N}$, we obtain 
\begin{equation}\label{elementsABS}
		\Psi^{'}(\bm{\tau})=\frac{1}{(1+L)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\lambda_{\tau_{x}}^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
\textbf{Remark:}  We aim to find equation \eqref{ABS_1} in the case $N=2$. For an arbitrary configuration $\bm{\tau}$, we have $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites (by indistinguishable particles) and the remaining $L-|\bm{\tau}|$ empty. We select $q\in\{0,\ldots,|\bm{\tau}|\}$ particles among the occupied ones. We call $\ell_{1},\ldots\ell_{q}\in \{1,\ldots,|\tau|\}$ such that $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$. These $(\ell_{i})_{i\in {1,\ldots,q}}$ are labels for the $q$ particles previously selected. For each $\ell_{i}$ we introduce $x_{\ell_{i}}$, i.e. the coordinate where the particle with label $\ell_{i}$ is placed. We this notation we have that 
	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{i=x_{\ell_{k}}}^{L}c_{i}\right)\dt
\subsubsection{Formula for exact correlations}\label{correlation-section}
	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle%=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
We observe that 
	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})
with $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$. Thus we have
	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
Denoting by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$ and recalling that  
	S_{1}^{T}=\prod_{x=1}^{L}d_{x}
we have
	\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle=\langle \bm{\tau}|D|\bm{\xi}\rangle \dt
Therefore, we have that 
	\mathbb{E}_{\mu^{\text{NESS}}}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
	=&\sum_{\bm{\tau}\in \Omega}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\nonumber\\
	=&\sum_{c_{1}=0}^{1}\ldots\sum_{c_{m}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\co
where in the second line we have used the resolution of the identity and in the last line we have used \eqref{ABS_1}. 
\subsection{The colour-blind case}
In this subsection we show that, if we stop distinguishing particles, we retrieve the non-equilibrium steady state correlations found in \cite{frassek2020eigenstates}. Moreover, for the sake of completeness, we also report the eigenvectors $|\Psi^{''}\rangle$ and $|\Psi^{'}\rangle$ when particles are indistinguishable.
\paragraph{Correlations of SSEP}
\paragraph{$|\Psi^{''}\rangle$ for SSEP}
\paragraph{$|\Psi^{'}\rangle$ for SSEP}
\subsection{Explicit formula for the steady state $|\Psi\rangle$}
{\color{blue}can we proceed as above? using sth similar to \eqref{goodTP-S2}}

@@

\subsubsection{Exact steady state correlations}
